### 2019-11-18 paper/introduction.tex
Methods edits except #26

Historically, the thermal-spectrum \gls{MSR} was designed for the Th/$^{233}$U
fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,
	merle2004scenarios,rosenthal1970molten}. This design assumes that we have
fissile $^{233}$U inventory to start up new \glspl{MSR}. However, $^{233}$U does not
exist in the Earth's crust and can only be produced from fertile $^{232}$Th in 
specific nuclear facilities. Therefore, we examine alternative fissile
materials to replace the $^{233}$U in the startup fuel
composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel
cycle transition can be achieved after reaching the doubling
time - time required to produce enough amount of $^{233}$U to trigger a
	new SD-TMSR - of $^{233}$U because in this case, all startup fissile material
is being substituted by newly produced $^{233}$U.

@@

%produce enough amount of $^{233}$U to start a new \gls{SD-TMSR}.
%Therefore, the aim of this paper is to operate the \gls{SD-TMSR} for a long 
%period of time with different initial fissile materials without external feed 
%of $^{233}$U (that does not exist anywhere) to produce enough amount of 
%$^{233}$U that is required to start a new \gls{SD-TMSR}.

%The \gls{MSR} is the only liquid-fueled reactor that the \gls{GIF} has chosen 
%as one of the six promising concepts 
%\cite{doe2002technology,pioro2016handbook}. The reactor's liquid fuel 
%distinguishes it from other nuclear reactors. \glspl{MSR} can operate 
%extended 
%time without shutdown for refueling with a superior neutron economy 
%\cite{doe2002technology}. Introducing online reprocessing and refueling 
%systems would ensure sustainability. In a \gls{MSR}, liquid fuel salt (e.g. a 
%mixture of LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) circulates through the core 
%and 
%transports fission heat to the \glspl{IHX}. Finally, this type of reactor has 
%a high conversion efficiency and a negative temperature coefficient.

%Both thermal and fast \gls{MSR} concepts exist in the literature 
%\cite{pioro2016handbook,engel1979development}. For thermal \glspl{MSR}, 
%hexagonal graphite prisms act as moderators. In contrast, fast spectrum 
%\glspl{MSR} lack moderators. A \gls{MSR} can breed in both cases, making them 
%optimal for realizing a desirable Thorium-Uranium fuel cycle 
%\cite{hargraves2010liquid}.

%In the 1950s, \gls{ORNL} performed experiments that provided a basis for 
%\gls{MSR} feasibility. In 1958, a 5 MW$_{th}$ homogeneous reactor experiment 
%called HRE-2 utilized water-based liquid fuel to illustrate the intrinsic 
%stability of homogeneous reactors. In the 1960s, \gls{ORNL} performed the 
%\gls{MSRE} 
%\cite{engel1979development,haubenreich1970experience,fiorinibasis,robertson1965msre}.
% These experiments demonstrated the capability of circulating a liquid 
%fluoride mixture without significant corrosion problems. Researchers used a 
%nickel-based alloy (Hastelloy N) as structural material and controlled the 
%fuel's oxidation by using a U$^{3+}$/U$^{4+}$ buffer. The experiment also 
%tested the continuous reprocessing of liquid fuel. The results showed that 
%introducing a noble gas system (i.e. gas bubbling system) during the fuel 
%cycle helps extract gaseous fission products \cite{pioro2016handbook}.

%\gls{ORNL} later researched the \gls{MSBR} \cite{rosenthal1970molten}. There 
%were two types of \gls{MSBR}: the single-fluid molten salt reactor and the 
%two-fluid molten salt reactor. While the single-fluid MSR dissolves fertile 
%and fissile materials in the same salt, the two-fluid MSR physically 
%separates 
%them. The two-fluid MSR had a higher breeding performance than the 
%single-fluid MSR. However, the single-fluid MSR can operate as an 
%iso-breeding 
%reactor as long as there is an efficient reprocessing system for the fuel 
%salt 
%\cite{rosenthal1970molten}.

%Despite the success of the \gls{MSRE}, \gls{ORNL} halted work on the 
%\gls{MSBR} in 1976. The \gls{Euratom} later revived the project. To enhance 
%the breeding performance of the \gls{MSBR}, \gls{Euratom} introduced the idea 
%of dividing the core into multiple zones of fuel channels with different 
%radii 
%\cite{nuttin2005potential}. The results showed that increasing the radii of 
%the outer fuel channels relative to the inner radii improved the reactor's 
%breeding and allowed it to out-perform the reactor with a single-zone core 
%and 
%large fuel channels \cite{nuttin2005potential}.

%Later, fast spectrum MSRs were introduced. Several fast MSR designs include: 
%\gls{MSFR}, \gls{EVOL} \cite{serp2014molten}, \gls{MOSART} 
%\cite{boussier2012molten}, REBUS-3700 \cite{mourogov2006potentialities} and 
%Molten Chloride Salt Fast Reactor \cite{taube1978fast}. \gls{GIF} has elected 
%to further research \gls{MSFR} and \gls{MOSART} 
%\cite{serp2014molten,boussier2012molten,locatelli2013generation,pettersen2016coupled}.
% Both designs feature the fast-spectrum, Th-based fuel, and liquid fuel 
%circulation. The \gls{MSFR} concept initially gained momentum at \gls{CNRS} 
%in 
%France, and the \gls{MOSART} concept is in progress in Russia.

%Indeed, several challenges interfere with the commercial adoption of 
%\gls{MSFR}. For example, large initial inventory of $^{233}$U and relatively 
%long doubling time for $^{233}$U production. Moreover, material scientists 
%must identify or create structural materials which have reasonable lifespan 
%in 
%extreme operational conditions (high temperature, large neutron flux, 
%chemically aggressive salt). Finally, breeding of high-quiality fissile 
%material in the \gls{MSFR} blanket rises significant nuclear 
%non-proliferation 
%concerns \cite{pettersen2016coupled,merle2009minimizing}.

%The thermal MSR has priority due to the low inventory of initial fissile 
%$^{233}$U and short doubling time for its production \cite{ZOU2015114}.
%Nagy et al. studied the effect of core zoning on the breeding performance and 
%graphite lifespan of a graphite-moderated MSR 
%\cite{nagy2011new,nagy2012effects}. Li et al. divided the active core into 
%two 
%zones to improve the breeding performance \cite{li_optimization_2018}. The 
%central zone is moderated, while the unmoderated outer zone acts as a 
%subcritical fast spectrum zone \cite{li_optimization_2018}.

%In 2011, the \gls{CAS} established the strategic project ``Future Advanced 
%Nuclear Energy $-$ Thorium-based Molten Salt Reactor System (TMSR)". Since 
%then, several studies aimed to improve the \gls{TMSR} to efficiently utilize 
%the Th-U fuel cycle 
%\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}.
%Separately, we can highlight the issue of a closed Th-U fuel cycle in the 
%thermal spectrum. A number of studies have shown the fundamental possibility 
%of organizing such a cycle in a heavy-water reactor and referred to the 
%limitation of the burn-up of solid fuels due to the accumulation of the 
%fission products (FPs) 
%\cite{dastur1995thorium,bergel2004mode,bergelson2008op}. The question of 
%feasibility and parameters of a closed U-Th fuel cycle in a \gls{TMSR} 
%reactor 
%is relevant.

%Liquid-fueled systems require specific neutron transport and depletion tools 
%that capture online fuel reprocessing and refueling. Specifically, the 
%circulation of the liquid fuel and the continuous feed or removal of elements 
%(e.g. fissile material injection into and Fission Products (FPs) extraction 
%from the fuel salt) are out-of-scope for most contemporary nuclear reactor 
%physics software, which was originally written primarily to simulate 
%solid-fueled reactors. The SERPENT-2 \cite{leppanen2014serpent} code 
%extension 
%takes into account the online fuel reprocessing and its effects on depletion 
%calculations \cite{aufiero2013extended}.

%The present paper aims to analyze the fuel depletion of the \gls{SD-TMSR} 
%during 60 years reactor operation time using SERPENT-2. This work 
%investigates 
%the inventory of isotopes in the core to establish the advantages of the 
%\gls{TMSR} concept applied to energy production (based on the thorium fuel 
%cycle). All calculations presented in the present work were implemented using 
%SERPENT-2 version 2.1.30. We adopted the built-in SERPENT-2 subroutine to 
%simulate continuous online reprocessing and refueling in contrast with other 
%batch-wise codes \footnote{In the batch-wise technique, the simulation stops 
%at a certain time and restarts after removing of poisoning isotopes and 
%addition of fissile and/or fertile materials.} (e.g. SaltProc 
%\cite{rykhlevskii2019modeling} and MCNP6-PYTHON \cite{Jeong2016}).
%SERPENT-2 allowed us to conduct burn-up calculations on computer clusters 
%with multiple cores using distributed-memory MPI parallelization. The drift 
%of 
%the delayed neutron precursors is not examined in this paper.

%The present paper is organized as follows: after a general introduction about 
%\gls{MSR} systems, section 2 briefly presents the \gls{SD-TMSR}. Section 3 
%focuses on the methodology and calculation tools used in this work. Fission 
%products extraction modeling is described in section 4. Section 5 highlights 
%the results and discussion. Finally, section 6 summarizes the conclusions.

>>>>

Historically, the thermal-spectrum \gls{MSR} was designed for the Th/$^{233}$U
fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,
	merle2004scenarios,rosenthal1970molten}. This design assumes that we have
fissile $^{233}$U inventory to start up new \glspl{MSR}. However, $^{233}$U does not
exist in the Earth's crust and can only be produced from fertile $^{232}$Th in 
specific nuclear facilities. Therefore, we examine alternative fissile
materials to replace the $^{233}$U in the startup fuel
composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel
cycle transition can be achieved after reaching the doubling
time $-$ time required to produce enough amount of $^{233}$U to trigger a
	new SD-TMSR $-$ of $^{233}$U because in this case, all startup fissile material
is being substituted by newly produced $^{233}$U.

@@
